ResultsNPS

### 2019-10-30 R/nps_reports/results.Rmd
added datasets and improved html reports graphs

```{r time_perf_graph} 
ggplot(data=comparison_table, aes(x=instance, y=time, color=experiment)) + theme_minimal() + geom_point(size=0.5)
```

@@

```{r time_perf_graph2} 
ggplot(data=comparison_table_reorder, aes(x=percentage, y=time, color=experiment)) + theme_minimal() + geom_point(size=0.5) + ggplot2::xlab('instance percentage')
```

>>>>

```{r time_perf_graph} 
ggplot(data=comparison_table, aes(x=instance, y=time, color=experiment)) + theme_minimal() + geom_point(size=0.5)+ theme(text = element_text(size=20))
```

@@

```{r time_perf_graph2} 
ggplot(data=comparison_table_reorder, aes(x=percentage, y=time, color=experiment)) + theme_minimal() + geom_point(size=0.5) + ggplot2::xlab('instance percentage') + theme(text = element_text(size=20))
```
